\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-10-27 paper/mswp2012-proposal.tex
englisch (zumindest versucht :) )

\providecommand*{\ShortTitle}{$<$Short title$>$}
\providecommand*{\FullTitle}{$<$Full title$>$}

@@

\author{
{\em 188.407: Management von Software Projekten} \vspace{1cm} \\
Group: $<$GID$>$\bigskip \\
$<$Author1$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author1@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author2$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author2@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author4$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author4@tuwien.ac.at}{author1@tuwien.ac.at}}\\ 
\vspace{4cm}
}

@@

\note{
\textbf{Formal constraints}
\begin{itemize}
\item	  Font: Times New Roman oder Computer Modern (\LaTeX default)
\item    Fontsize: 11pt
\item     Single line spacing
\item     Margins: 2.5cm side and top/bottom
\item     \fbox{Language: ENGLISH}
\item    The proposal template should be filled incrementally. I.e., at the end there should be a full project proposal in a single PDF file.
\end{itemize}
\textbf{Available templates}
\begin{itemize}
\item     Proposal (mswp-proposal.tex)
\item     Costs (costs.xls, costs.ods)
\end{itemize}
\textbf{Supplemental material}
\begin{itemize}
\item     FWF salary scheme (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
\item     Travel cost regulation (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html})
\item     Ethical issues form (ethical-issues.rtf)
\end{itemize}
}
\pagebreak

@@

Das Projekt verfolgt das Ziel eine Plattform im Bereich e-Health zu schaffen. Diese Platform soll für die Nutzer ein Bonus-System bereitstellen und die Möglichkeit bieten herauszufinden, wie gesund die einzelnen Nutzer leben.\\

Das Projekt wird hierbei in verschiedene Phasen aufgeteilt, die eine langfristige Weiterentwicklung möglich machen bzw. mögliche Ausbaustufen aufzeigen. Für jeden der Phasen müssen Vertragspartner gefunden werden, die sich an der Plattform beteiligen. Diese Vertragspartner versorgen die Nutzer mit Boni und bekommen als Benefit eine Steigerung der Kundenbindung bzw. eine Möglichkeit Werbepräsenz auf der Plattform zu ergattern.\\

Mögliche Vertragspartner sind:
\begin{itemize}
	\item Phase 1:
		\begin{itemize}
			\item Supermärkte
			\item Fitness-Center
			\item Restaurants
		\end{itemize}
	\item Phase 2 - \"Einbindung bestehender Services\":
		\begin{itemize}
			\item Laufplattformen mit Tracking (Runtastic, RunKeeper, etc.)
			\item andere Sporttracking-Services (Schrittzähler, etc.)
		\end{itemize}
	\item Phase 3 - \"Health Organisations\":
		\begin{itemize}
			\item Versicherungsunternehmen
		\end{itemize}
\end{itemize}

Die Nutzer haben die Möglichkeit beim Einkauf oder Konsumation bei einem der Vertragspartner selbiges über eine App registrieren lassen. Im System werden dann anonymisiert die Einkäufe in Kategorien gespeichert und nach einem vorgefertigtem transparenten Punkteschmea bewertet.\\

Die Punkte können nach einer bestimmten Zeitspanne durch Gutscheine eingelöst werden, die dann bei den Vertragspartnern wieder eingelöst werden können. Ebenso können über die Plattformen Rankings und Verlosungen vorgenommen werden. Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.

>>>>

\providecommand*{\ShortTitle}{Modern voluntary health-care-system}
\providecommand*{\FullTitle}{$<$Full title$>$}

@@

\author{
{\em 188.407: Management von Software Projekten} \vspace{1cm} \\
Group: 12\bigskip \\
Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
Dominik Oberhumer \\ {\small 1025454, 033 534, \href{mailto:e1025454@student.tuwien.ac.at}{e1025454@student.tuwien.ac.at}}\\
$<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author4$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author4@tuwien.ac.at}{author1@tuwien.ac.at}}\\ 
\vspace{4cm}
}

@@

%\note{
%\textbf{Formal constraints}
%\begin{itemize}
%\item	  Font: Times New Roman oder Computer Modern (\LaTeX default)
%\item    Fontsize: 11pt
%\item     Single line spacing
%\item     Margins: 2.5cm side and top/bottom
%\item     \fbox{Language: ENGLISH}
%\item    The proposal template should be filled incrementally. I.e., at the end there should be a full project proposal in a single PDF file.
%\end{itemize}
%\textbf{Available templates}
%\begin{itemize}
%\item     Proposal (mswp-proposal.tex)
%\item     Costs (costs.xls, costs.ods)
%\end{itemize}
%\textbf{Supplemental material}
%\begin{itemize}
%\item     FWF salary scheme (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}%{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
%\item     Travel cost regulation (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html})
%\item     Ethical issues form (ethical-issues.rtf)
%\end{itemize}
%}
%\pagebreak

@@

The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system for the users. So the users are able to find out how healthy they life. \\

The project is split into different phases. This enables a useable product after a short time but the vision is a long-term development. For each phase it is necessary to find different partner in economy and politics. The partners use the platform for advertisement and for costumer relationship. So the partners have benefits too. \\

Possible Partners are:
\begin{itemize}
	\item Phase 1:
		\begin{itemize}
			\item Supermarkets
			\item Fitness-Centers
			\item Restaurants
		\end{itemize}
	\item Phase 2 - $"$Embedding to existing services$"$:
		\begin{itemize}
			\item Sport-Community with Tracking (Runtastic, RunKeeper, etc.)
			\item other Sporttracking-Services (Pedometer, etc.)
		\end{itemize}
	\item Phase 3 - $"$Health Organisations$"$:
		\begin{itemize}
			\item Insurances 
		\end{itemize}
\end{itemize}

When a user buys something in a shop of a partner he can register the products within an App. In the System the consummations get anonymised saved and analyzed based on a transparent score-schema. \\

The user can exchange the scores for gifts like coupons for healthy shopping by a partner. Moreover the platform can be used for rankings (which of the user live most healthy?) and lotteries. The partner can interact with the user over the platform. So they can advertise new promotions. This promotion can be used by the user for getting additional scores. \\

The goals of the platform:
\begin{itemize}
\item \textbf{Health of the User}: The peoples are getting more sensible for health-care. So they are going to live in a healthier way. The healthcare-system is very expansive. So the whole government will have a benefit from this platform and more healthier people. 
\item \textbf{Advertisment for the Partner}: For the partner the platform offers a chance to advertise their promotions. Furthermore they have the chance to spend coupons to the user. With this coupon they can interact with the costumer. So the customer loyalty is getting gain. The costumer is getting animated to buy more by partners. For this the partner has to refinance a part of the platform. 
\item \textbf{Benefits for User}: The User should get cheaper prices, when they buy some healthy things within partner stores. For example the coupons from an lottery in this platform.

\end{itemize}
